R Notebook

### 2018-02-21 paper/docs/04_Modelresults.Rmd
k=40

```{r echo = FALSE}
load("../output/models/STM 40 .Rda")
k <- stmOut$settings$dim$K
```

@@

@@

The plotQuote function allows to inspect die most common words of a topic for each covariate. Here I check for topic 3 (Jamaica coalition)

@@

```{r fig.width=12}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
  geom_col(fill = col[3]) +
  #scale_fill_manual(values = col[1]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
dpi = 600)
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Tokenize text
token <- btw.2 %>%
  filter(gamma >= 0.9) %>%
  filter(topic %in% keep) %>%
  unnest_tokens(word, text)

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(sentiment = as.numeric(value)) %>% 
  filter(!is.na(sentiment)) 
```

#### 3. Calculate sentiment value

>>>>

```{r echo = FALSE}
load("../output/models/STM 45 .Rda")
k <- stmOut$settings$dim$K
```

@@

The plotQuote function allows to inspect die most common words of a topic for each covariate.

@@

@@

```{r fig.height=8, fig.width=12}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
  geom_col(fill = col[3]) +
  #scale_fill_manual(values = col[1]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

# ggsave(plot = p1, filename = "../figs/estimates.png", device = "png",width = 10, height = 7,
# dpi = 600)
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Tokenize text
token <- btw.2 %>%
  filter(gamma >= 0.75) %>%
  filter(topic %in% keep) %>%
  unnest_tokens(word, text)

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(value = as.numeric(value)) %>% 
  filter(!is.na(value)) %>%
  mutate(polarity = ifelse(value < 0, "negative", "positive"))
```

#### 3. Calculate sentiment value by document

calculate sentiment value of document $d$:

$$
\text{Sentiment}_d = \frac{|\text{Sum of positive tokens}_d| - |\text{Sum of negative tokens}_d|}{\text{Number ot tokens}_d}
$$

```{r}
sentDF.values <- sentDF %>%
  select(document, word, value, polarity) %>%
  mutate(id = row_number()) %>%
  spread(polarity, value) %>%
  group_by(document) %>%

  # calculate sum of positive and negative values
  summarise(sum_positive = sum(positive, na.rm = T),
            sum_negative = sum(negative, na.rm = T)) %>%
  ungroup() %>%
  # calculate diff
  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%
  # combine with dataframe
  left_join(., btw.2 %>% filter(topic %in% keep), 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment = sent_diff / text_length)
```

#### 4. Inspect sentiment value

```{r fig.width=8, fig.height=12}
p <- sentDF.values %>%
  group_by(topic_name, date, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T))

p %>%
  filter(grepl("Merkel", topic_name)) %>%
  ggplot(aes(date, sentiment,
              fill = factor(topic_name))) +
  geom_col() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  facet_wrap(~site, ncol = 1) +
  labs(x="", y="", fill="") +
  theme(legend.position = "right")
```

### 2018-02-21 paper/docs/04_Modelresults_35.Rmd
k=40

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 12,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      panel.border = element_blank()
    )
)

@@

```{r echo = FALSE}
load("../output/models/STM 45 .Rda")
k <- stmOut$settings$dim$K
```

@@

In order to improve readability and traceability, I assign a shorter name to the topics based on the most common words.

```{r}
sagelabs <- sageLabels(stmOut, 20)

sagelabs$cov.betas[[3]]$problabels[,1:6]
```

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 
                   4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results",
                   8, "Party congress (CSU and DIE LINKE)", 9, "General societal issues", 
                   10, "Information on Federal elections (e.g. Wahlomat, election programmes)",  
                   11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')",
                   14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 
                   16, "Great coalition, minority government", 17, "AfD, in media", 18, "Jamaica coalition", 
                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter", 
                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)", 
                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag", 
                   27, "Mix, Surveys, public statistics", 28, "Election polls", 
                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 
                   31, "German armed forces, v.d.Leyen", 
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 
                   39, "Statistics, welfare policy",
                   40, "J.Spahn"), ncol=2, byrow=T)

# topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
#                    5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
#                    9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
#                    11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
#                    14, "B90/Die Grüne", 
#                    15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
#                    18, "Budget statistics, Welfare policy", 
#                    19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
#                    22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
#                    25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
#                    27, "Surveys, public statistics", 28, "Election polls", 
#                    29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
#                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
#                    34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)

@@

The plotQuote function allows to inspect die most common words of a topic for each covariate.

```{r fig.height=11, fig.width=5}
topic <- 40

@@

#### Inspect the unclear topics
```{r}
btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  top_n(10) %>%
  htmlTable::htmlTable(align="l")
```

```{r}
btw.2 %>% filter(topic==10) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  top_n(10) %>%
  htmlTable::htmlTable(align="l")
```

@@

Keep only those articles, that are clear

```{r}
keep <- c(1,2,3,4,5,6,7,12,14,15,16,17,18,21,23,24,28,29,31,32,33,34,35,38,40)
```

@@

freq <- freq %>%
  left_join(., topics.df, by = "topic") %>%
  filter(topic %in% keep) %>%
  mutate(topic = topic_name) %>%
  left_join(., frequency %>% select(topic, frequency),
            by = "topic")
```

@@

```{r fig.height=8, fig.width=12}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
  geom_col(fill = col[3]) +
  #scale_fill_manual(values = col[1]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

The following figure shows the regression results for each news page. The coefficients indicate the deviation from the base value of Bild.de.

@@

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Tokenize text
token <- btw.2 %>%
  filter(gamma >= 0.75) %>%
  filter(topic %in% keep) %>%
  unnest_tokens(word, text)

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(value = as.numeric(value)) %>% 
  filter(!is.na(value)) %>%
  mutate(polarity = ifelse(value < 0, "negative", "positive"))
```

@@

  # calculate sum of positive and negative values
  summarise(sum_positive = sum(positive, na.rm = T),
            sum_negative = sum(negative, na.rm = T)) %>%
  ungroup() %>%
  # calculate diff
  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%
  # combine with dataframe
  left_join(., btw.2 %>% filter(topic %in% keep), 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment = sent_diff / text_length)
```

#### 4. Inspect sentiment value

```{r fig.width=8, fig.height=12}
p <- sentDF.values %>%
  group_by(topic_name, date, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T))

p %>%
  filter(grepl("Merkel", topic_name)) %>%
  ggplot(aes(date, sentiment,
              fill = factor(topic_name))) +
  geom_col() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  facet_wrap(~site, ncol = 1) +
  labs(x="", y="", fill="") +
  theme(legend.position = "right")
```

calculate weight:

$$
\text{weight} = \frac{\text{Total Articles, by site & topic}}{\text{Total Articles, by site}}
$$

```{r}
# Calculate weight
btw.2 <- btw.2 %>%

  # how many articles per site & topic?
  group_by(site, topic) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(count = n) %>%
  select(-n) %>%

  # how many articles per site?
  group_by(site) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(totalcount = n) %>%
  select(-n) %>%

  # calculate weight
  mutate(weight = count/totalcount)
```

Group by article ID and calculate the mean sentiment value of each article.

```{r}
sentDF.red <- sentDF %>%

  # calculate weight and weighted sentiment score
  group_by(articleID) %>%
  summarise(sent_value = mean(sentiment)) %>%

  # leftjoin with btw
  left_join(., btw.2 %>% select(articleID, topic, topic_name,
                                title, url, site, gamma, weight),
            by="articleID") %>%
  mutate(weighted = sent_value*weight)
```

```{r}
sentDF.red %>% group_by(topic_name) %>%
  top_n(5, gamma) %>%
  select(topic_name, gamma, title) %>%
  htmlTable::htmlTable(align="l")
```

@@

#### 1. by topic
```{r fig.height=10, fig.width=12}
p1 <- sentDF.red %>%
  group_by(topic_name, topic) %>%
  summarise(sent_value = mean(sent_value)) %>%
  ggplot(aes(reorder(topic_name, sent_value), sent_value)) +
  geom_col(fill=col[3], alpha=0.8) +
  coord_flip() +
  labs(x="", y="sentiment value (unweighted)",
       title = "sentiment value (unweighted)") +
  theme(
        axis.text.y = element_text(size = 10))

p2 <- sentDF.red %>%
  group_by(topic_name, topic) %>%
  summarise(weighted = mean(weighted),
            sent_value = mean(sent_value)) %>%
  ggplot(aes(reorder(topic_name, sent_value), weighted)) +
  geom_col(fill=col[1], alpha=0.8) +
  coord_flip() +
  labs(x="", y="sentiment value (weighted)",
       title = "sentiment value (weighted)") +
  theme(
        axis.text.y = element_blank())

p1 + p2
```

@@

```{r fig.width=12}
p1 <- sentDF.red %>%
  group_by(site) %>%
  summarise(sent_value = mean(sent_value)) %>%
  ggplot(aes(reorder(site, sent_value), sent_value)) +
  geom_col(fill=col[3], alpha=0.8) +
  coord_flip() +
  labs(x="", y="sentiment value (unweighted)",
       title = "sentiment value (unweighted)") +
  theme(
        axis.text.y = element_text(size = 10))

p2 <- sentDF.red %>%
  group_by(site) %>%
  summarise(weighted = mean(weighted),
            sent_value = mean(sent_value)) %>%
  ggplot(aes(reorder(site, sent_value), weighted)) +
  geom_col(fill=col[1], alpha=0.8) +
  coord_flip() +
  labs(x="", y="sentiment value (weighted)",
       title = "sentiment value (weighted)") +
  theme(
        axis.text.y = element_blank())

p1 + p2
```

@@

```{r fig.height=10, fig.width=12}
sentDF.red %>%
  group_by(site, topic_name, topic) %>%
  summarise(sent_value = mean(sent_value)) %>%
  ggplot(aes(reorder(topic_name, topic), sent_value)) +
  geom_col(fill=col[3], alpha=0.8) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="sentiment value (unweighted)",
       title = "sentiment value (unweighted)") +
  theme(axis.text.y = element_text(size=12))

ggsave(filename = "../figs/sent_weighted.png", device = "png",width = 12, height = 8,
dpi = 600)
```

```{r fig.height=10, fig.width=12}
sentDF.red %>%
  group_by(site, topic_name, topic) %>%
  summarise(weighted = mean(weighted)) %>%
  ggplot(aes(reorder(topic_name, topic), weighted)) +
  geom_col(fill=col[1], alpha=0.8) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="sentiment value (weighted)",
       title = "sentiment value (weighted)") +
  theme(axis.text.y = element_text(size=12))
```

@@

Select topics to be analyzed:

1: "SPD, M.Schulz"
2: "A.Merkel vs. Schulz"
3: "Jamaica coalition"
6: "A.Merkel"
8: "CSU, Seehofer, Söder"
14: "B90/Die Grüne"
16: "Great coalition"
17: "AfD, in social media",
24: "CDU, social media"
29: "AfD"

1, "SPD, M.Schulz"
2, "A.Merkel vs. Schulz"
3, "B90/Die Grüne, coalition talks"
4, "EU policies"
5, "H.Kohl", 
6, "A.Merkel", 
8, "CSU, Seehofer, Söder",
12, "Refugees in GER"
14, "B90/Die Grüne, climate/refugee policy",
16, "Great coalition", 
17, "AfD, in media", 
18, "Jamaica coalition",
29, "AfD",
33, "Diplomatic relations w Turkey, Russia",
35, "CDU/CSU H.Seehofer, Obergrenze",
38, "AfD, F.Petry")

```{r}
#keep <- c(1,2,3,6,8,14,16,17,24,29)

keep <- c(1,3,4,5,6,8,14,16,17,18,29,33,35,38)
```

#### Unweighted
```{r}
sentDF.red %>% 
  filter(topic %in% keep) %>%
  group_by(site, topic_name) %>%
  summarise(sent_value = mean(sent_value)) %>%
  spread(key=topic_name, value=sent_value) %>%
  ungroup() -> radar

@@

#### Weighted
```{r}
sentDF.red %>% 
  filter(topic %in% keep) %>%
  group_by(site, topic_name) %>%
  summarise(weighted = mean(weighted)) %>%
  spread(key=topic_name, value=weighted) %>%
  ungroup() -> radar

>>>>

theme_set(
  theme_bw(base_family = "Roboto", base_size = 10) +
    theme(
      plot.title = element_text(size = 14,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 8),
      plot.caption = element_text(size = 6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      panel.border = element_blank()
    )
)

@@

```{r echo = FALSE}
load("../output/models/STM 35 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

In order to improve readability and traceability, I assign a shorter name to the topics based on the most common words.
The plotQuote function allows to inspect die most common words of a topic for each covariate.

```{r eval=FALSE, fig.height=12, fig.width=5, include=FALSE}
topic <- 45

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs. Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)

@@

@@

#### Inspect the unclear topics
```{r eval=FALSE, include=FALSE}
btw.2 %>% filter(topic==13) %>% select(title, gamma, url) %>%
  arrange(desc(gamma)) %>%
  top_n(10) %>%
  htmlTable::htmlTable(align="l")
```

@@

Keep only those articles, that are clear & interessting to analyse.

```{r}
keep <- c(1,2,6,8,14,16,17,18,24,29,31,35,38,40,41,43)
```

@@

freq <- freq %>%
  left_join(., topics.df, by = "topic") %>%
  #filter(topic %in% keep) %>%
  mutate(topic = topic_name) %>%
  left_join(., frequency %>% select(topic, frequency),
            by = "topic")
```

@@

```{r fig.height=8, fig.width=12}
p2 <- ggplot(freq, aes(reorder(topic_name,frequency), freq)) +
  geom_col(fill = col[3]) +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  theme(
    #axis.text.y = element_blank(),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="expected frequency")

@@

The following figure shows the regression results for each news page. The coefficients indicate the deviation from the base value of Bild.de (keeping the month equal).

@@

The following figure shows the regression results for each month. The coefficients indicate the deviation from the base value of June 2017 (keeping the news source).

```{r fig.height=8, fig.width=12}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(!parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  filter(parameter != "(Intercept)") %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.75) %>%
  filter(topic %in% keep)

# Tokenize text
token <- df %>%
  unnest_tokens(word, text)

# Combine with sentiment values
sentDF <- left_join(token, sent, by="word") %>% 
  mutate(value = as.numeric(value)) %>% 
  #filter(!is.na(value)) %>%
  mutate(polarity = ifelse(value < 0, "negative", "NA"),
         polarity = ifelse(value > 0, "positive", polarity))
```

@@

  # calculate sum of positive and negative values
  summarise(sum_positive = sum(positive, na.rm = T),
            sum_negative = sum(negative, na.rm = T)) %>%

  # calculate diff
  mutate(sent_diff = abs(sum_positive) - abs(sum_negative)) %>%

  # combine with dataframe
  left_join(., df, 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment = sent_diff / text_length)
```

@@

#### 1. by topic
```{r fig.height=8, fig.width=6}

p <- sentDF.values %>%
  group_by(topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment)) +
  geom_col(aes(fill=p$obs)) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

@@

```{r}
p <- sentDF.values %>%
  group_by(site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, aes(reorder(site, sentiment), 
              sentiment)) +
  geom_col(aes(fill=p$obs)) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Grouped Sentiment value",
       fill = "Number of\nObservations") +
  theme(axis.text.y = element_text(size = 10))
```

@@

```{r fig.height=8, fig.width=12}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n())

ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment)) +
  geom_col(aes(fill=p$obs)) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="", fill= "Number of\nObservations",
       title = "Sentiment value") +
  theme(axis.text.y = element_text(size=12))
```

@@

```{r}
sentDF.values %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
  spread(key=topic_name, value=sentiment) -> radar

@@

```{r}
for (i in stmOut$settings$covariates$yvarlevels) {

  p <-radar %>%
    filter(site == i) %>%
    ggRadar(rescale = F,
            alpha = 0, legend.position = "right") +
    labs(title = i)

  ggsave(p, filename = paste0("../figs/radarchart_",i,k,".png"), 
         device = "png", dpi = 600)

}

<img src="../figs/radarchart_Bild.de45.png", width = "45%">
<img src="../figs/radarchart_DIE WELT45.png", width = "45%">
<img src="../figs/radarchart_FOCUS ONLINE45.png", width = "45%">
<img src="../figs/radarchart_SPIEGEL ONLINE45.png", width = "45%">
<img src="../figs/radarchart_stern.de45.png", width = "45%">
<img src="../figs/radarchart_Tagesschau.de45.png", width = "45%">
<img src="../figs/radarchart_ZEIT ONLINE45.png", width = "45%">

### 2018-02-21 paper/docs/04_Modelresults_40.Rmd
k=40

```{r echo = FALSE}
load("../output/models/STM 35 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 5, "H.Kohl", 6, "Federal Elections", 7, "EU policies, refugees", 8, "Political trends in GER", 9, "AfD in Parliament", 10, "A.Merkel", 11, "Hamburg G20", 12, "Christian, Berlin, Bruch", 13, "Climate policy, Die Grünen", 14, "Seehofer vs. Söder", 15, "D.Trump", 16, "Great coalition", 17, "CDU/CSU", 18, "Elections in Niedersachen", 19, "Budget statistics, Welfare policy", 20, "AfD in social media", 21, "DIE LINKE", 22, "German armed forces, Mali", 23, "Weather, Bahn", 24, "Innenministerium, Verfassungsschutz", 25, "Terror attack (Amri)", 26, "G20 in Hamburg", 27, "Spahn (CDU)", 28, "Steinmeier", 29, "German armed forces", 30, "AfD", 31, "Women empowerment", 32, "Diplomatic relations w Turkey, Russia", 33, "Election polls", 34, "Votings in parliament", 35, "F.Petri, Staatsanwaldschaft"), ncol=2, byrow=T)

>>>>

```{r echo = FALSE}
load("../output/models/STM 40 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks",
4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel",
7, "Federal Election results", 8, "Party congress (CSU and DIE LINKE)",
9, "General societal issues", 10, "Information on Federal elections (e.g. Wahlomat, election programmes)",
11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')", 14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 16, "Great coalition, minority government", 17, "AfD, in media", 
                   18, "Jamaica coalition",
                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter",
                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)",
                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag",
                   27, "Mix, Surveys, public statistics", 28, "Election polls",
                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen",
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia",
                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
                   40, "J.Spahn"), ncol=2, byrow=T)

### 2018-02-21 paper/docs/04_Modelresults_45.Rmd
k=40

```{r echo = FALSE}
load("../output/models/STM 40 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks",
4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel",
7, "Federal Election results", 8, "Party congress (CSU and DIE LINKE)",
9, "General societal issues", 10, "Information on Federal elections (e.g. Wahlomat, election programmes)",
11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')", 14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 16, "Great coalition, minority government", 17, "AfD, in media", 
                   18, "Jamaica coalition",
                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter",
                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)",
                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag",
                   27, "Mix, Surveys, public statistics", 28, "Election polls",
                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen",
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia",
                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
                   40, "J.Spahn"), ncol=2, byrow=T)

>>>>

```{r echo = FALSE}
load("../output/models/STM 45 .Rda")
k <- stmOut$settings$dim$K
sagelabs <- sageLabels(stmOut, 20)
```

@@

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica, fail of coalition talks, reelections",
                   4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel",
                   7, "Federal Election results", 8, "Party congress CSU",
                   9, "Mix: political trends, Macron (FR), EU", 
                   10, "Information on Federal elections (e.g. Wahlomat, election programmes)", 
                   11, "politics & democracy in GER", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')", 
                   14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 
                   16, "Great coalition, minority government", 17, "AfD, in media", 18, "Jamaica coalition talks", 
                   19, "Rubbish", 20, "Mix (Amri, Schmähgedicht Böhmermann)", 21, "German armed forces, Aviation", 
                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU", 
                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag", 
                   27, "Mix, Surveys, public statistics", 
                   28, "Election polls", 29, "AfD, Gauland", 30, "Sexism, abuse of women & children", 
                   31, "German armed forces, v.d.Leyen", 32, "G20 in Hamburg",
                   33, "Diplomatic relations w Turkey, Russia", 
                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, refugee cap",
                   36, "Mix: A.Merkel in Saxony, Weather", 37, "Car industry, Stuttgart, Mix", 38, "AfD, F.Petry", 
                   39, "Statistics, welfare policy", 40, "Jamaica", 41, "AfD, Höcke", 42, "Religion (Muslim, Christ)", 
                   43, "AfD Fraktion im Bundestag", 44, "Ermittlungen Bundesanwaltshaft (NSU, Franco, Terror)", 
                   45, "Berlin capital"), ncol=2, byrow=T)

### 2018-02-21 paper/writing/structure.tex
k=40

>>>>

\subsection{Sentiment Analysis}

The idea of Sentiment analysis is to determine the attitude of a writer through online text data toward certain topic or the overall tonality of a document.

commonly used lexical or “bag-ofwords” approach. In that approach, the researcher provides pre-defined dictionaries (lists) of words associated with a given emotion, such as negativity. The target text is then deconstructed into individual words (or tokens) and the frequencies of words contained in a given dictionary are then calculated. For example, Loughran and McDonald (2011) construct a dictionary of words that express negativity in financial contexts, which they then use to measure the negativity in company 10-K filings and relate that negativity to financial outcomes.

The psychology literature demonstrates that any emotion can be parsimoniously defined by assigning it a score along two primary dimensions: valence (i.e., positive or negative) and arousal (i.e., activation and deactivation). For comparison purposes, we also examine three additional measures: “worried,” “satisfied,” and a lexical “negativity” measure.

In financial market research: 
\citep{nyman_news_2018}: This paper applies algorithmic analysis to large amounts of financial market text-based data to assess how narratives and sentiment play a role in driving developments in the financial system. For the summary statistic of a collection of texts T, we count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters:

\begin{equation}
	\text{Sentiment}[T]=\frac{|\text{Excitement}|-|\text{Anxiety}|}{\text{size}[T]}
\end{equation}

Simplicity of this method also allows for an easier assessment of the robustness of the methodology: The apply a bootstrap technique to compute 95\% confidence intervals around the summary statistic. We sample new weights for each word in each dictionary (so that the sum of weights equals the size of the dictionary) and re-compute the statistic. Repeating the procedure gives a distribution from which to extract the confidence intervals. This technique gives us increased confidence that the meaning of individual words in our two lists does not change over time. Obviously, one can also imagine other methods of extracting confidence levels, e.g., to sample with replacement from the collection of texts.
